An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-06-14 tex/response.tex

Some of these we comment here for ease of review:

Documentation paragraph in the prob end tournament section has been fixed. It
now reads:

\begin{quote}
    We can also view the length of the matches played by each player. The plot
    shows that the length of each match (for each player) is not the same. The
    median length is 4 which is the expected value with the probability of a
    match ending being 0.5.
\end{quote}

The copyright section of the license has been reworded. A discussion of this can
be viewed here: \url{https://github.com/Axelrod-Python/Axelrod/issues/615}.

@@

The code snippets that were not complete (final line for plotting) have been
fixed. Furthermore, an explanation of how to obtain the full tournament results
has also been included.

The discussion group has been made public. This was an oversight.

Regarding the urls that were not correct in the bibliography: we have removed
these for the present time and will leave the formatting/requirements for these
till the editorial process. Note that the ones we have removed correspond to
well referenced published pieces of work and so removing the urls does not
hinder finding the sources.

One comment we have not addressed is with regards to hypothesis not being a
requirement.  Hypothesis is a requirement for development. Cloudpickle is no
longer a requirement following some substantial rewriting of the internals of
the library (resulting in speed, memory and readability improvements).
TestFixtures is also, no longer a requirement.

Other changes include updating the figures showing the number of strategies and
the latest run of the tournament as well as including another author: due to the
fact that they contributed a new strategy while the paper was under review.

Furthermore, we have made some minor changes to the text. These were all minor
typographical changes aimed at improving the readability of the manuscript.
